The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with {\em Gaia} Data and Beyond

### 2019-05-04 paper/ms.tex
Update rationale for ignoring LSR variations

\subsection{Velocity Variations} \label{ssec:lsr_var}
We also expect that the local standard of rest (LSR) should vary as a function
of azimuth. We perform this calculation in Appendix~\ref{app:lsr} to estimate
the components of the LSR as a function of azimuth, but performing a best-fit
subtraction to correct for misalignment of the original coordinate system (as
in the previous section) is more involved. Since we find that the variation in
the LSR is less pronounced than for the midplane, and since the dominant
effect is limited to $J_R$ (Figure~\ref{fig:many_orbit_wrong_ref}), we defer
this calculation to future work.

>>>>

\subsection{Velocity Variations} \label{ssec:lsr_var}
We also expect that the local standard of rest (LSR) should vary as a function
of azimuth. We perform this calculation in Appendix~\ref{app:lsr} to estimate
the components of the LSR as a function of azimuth, but performing a best-fit
subtraction to correct for misalignment of the original coordinate system (as
in the previous section) is more involved. Since we find that the variation in
the LSR is less pronounced than for the midplane, and since offsets in
velocity only contribute to second order to $J_R$ and $J_z$ when a star is at
maximum amplitude in $R$ or $z$ (where the majority of the orbit is, see
Section~\ref{ssec:epi_action}), we defer this calculation to future work.
